### 2021-04-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

\textit{Cryptography Applications:} Our benchmarks include the most popular cryptography libraries, such as mebdTLS, OpenSSL, Libgcropt, and wolfSSL. We divide ciphers into three categories: stream ciphers, symmetric ciphers, and asymmetric ciphers. For stream ciphers, we use RC4. For symmetric ciphers, we choose AES. We also evaluate the tool on RSA, a widely used algorithm in the public-key cryptosystem.

@@

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Leaked Functions}} & \multicolumn{2}{c}{\textbf{Max. Leak (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  64 Bytes & 1 Byte  & 64 Bytes & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
Unsafe Password Checker& 65536& 16.0& 1&0&0.04&  0& 18 & 104 KB & 21 min & 0.4 min & 0 min\\
Safe Password Checker & 65536 & 16.0& 0&0 &0 &0 & 20 & 106 KB & 20 min & 0.4 min & 0 min\\
One-byte Lookup Table & 65536 & 16.0& 1&1&9.8& 3.6 & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
Four-byte Lookup Table & 65536 & 16.0& 1&1&9.6& 8.5 & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
AES T-Table mbedTLS 2.15 & 65536 & 16.0&2&2&11.6 &6.7& -& 1.1 MB &65 min & 0.8 min & 0.1 min  \\
AES NI mbedTLS 2.15 & 65536 & 16.0&0&0&0 &0&-& 1.1 MB & 45 min & 0 min & 0 min  \\
AES OpenSSL 1.1.0  & 65536 & 16.0 & 2&0 &1.4 & 0&-& 1.0 MB  & 49 min & 0.2 min & 0 min \\
AES  OpenSSL 1.1.1& 65536 & 16.0 & 2&0 &1.3&0&-& 909 KB & 46 min & 0.2 min & 0 min\\
AES  wolfSSL 4.5.0& 65536 & 16.0 &2&0& 0.11& 0 & - &1.1 MB & 53 min & 0.1 min & 0 min \\
AES Libgcrypt 1.8.7& 65536 & 16.0 &0 &0 &0&0 &-&4.4 MB & 164 min& 0 min & 0 min\\
RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB\\
RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&6.7& 4.1 &-& 11 MB\\
RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&-&13 MB\\
RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&-&4.2 MB\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&-&4.4 MB\\
Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB \\
GDK 3.24.23 & 65535 & 16.0 & 33&31& 12.1& 6.0&-& 48 MB\\
\bottomrule
\end{tabular}
}

@@

\subsection{Result Overview}
Table~\ref{chapter5:table:over_result} presents the overview result.

>>>>

\textit{Cryptography Applications:} Our benchmarks include the most popular cryptography libraries, such as mebdTLS, OpenSSL, Libgcropt, and wolfSSL. Encryption ciphers can be divided into three categories:  symmetric ciphers, and asymmetric ciphers. For stream ciphers, we use RC4. For symmetric ciphers, we choose AES. We also evaluate the tool on RSA, a widely used algorithm in the public-key cryptosystem.

@@

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Leaked Functions}} & \multicolumn{2}{c}{\textbf{Max. Leak (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  64 Bytes & 1 Byte  & 64 Bytes & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
Unsafe Password Checker& 4096& 12.0& 1&0&0.04&  0& 18 & 104 KB & 2.4 min & 0.4 min & 0 min\\
Safe Password Checker & 4096 & 12.0& 0&0 &0 &0 & 20 & 106 KB & 2.3 min & 0.4 min & 0 min\\
One-byte Lookup Table & 4096 & 12.0& 1&1&9.8& 3.6 & 18 & 104 KB & 0.8 min & 0.1 min & 0 min\\
Four-byte Lookup Table & 4096 & 12.0& 1&1&9.6& 8.5 & 18 & 104 KB & 0.7 min & 0.1 min & 0 min\\
AES T-Table mbedTLS 2.15 & 4096 & 12.0&2&2&11.6 &6.7& -& 1.1 MB &4.1 min & 0.8 min & 0.1 min  \\
AES NI mbedTLS 2.15 & 4096 & 12.0&0&0&0 &0&-& 1.1 MB & 2.8 min & 0 min & 0 min  \\
AES OpenSSL 1.1.0  & 4096 & 12.0 & 2&0 &1.4 & 0&-& 1.0 MB  & 3.1 min & 0.2 min & 0 min \\
AES  OpenSSL 1.1.1& 4096 & 12.0 & 2&0 &1.3&0&-& 909 KB & 2.9 min & 0.2 min & 0 min\\
AES  wolfSSL 4.5.0& 4096 & 12.0 &2&0& 0.11& 0 & - &1.1 MB & 3.3 min & 0.1 min & 0 min \\
AES Libgcrypt 1.8.7& 4096 & 12.0 &0 &0 &0&0 &-&4.4 MB & 10.2 min& 0 min & 0 min\\
RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB& 1321.1 min & 63.5 min & 5.1 min \\
RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&6.7& 4.1 &-& 11 MB & 981.1 min & 75.4 min & 4.5 min\\
RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&-&13 MB & 1021.1 min & 45.1 min & 5.5 min\\
RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&-&4.2 MB & 1613.6 min & 51.6 min & 7.9 min\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&-&4.4 MB & 1412.6 min & 23.9 min & 4.3 min\\
Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB & 183.5 min & 24.6 min & 5.2 min\\
GDK 3.24.23 & 4096 & 16.0 & 33&31& 12.1& 6.0&-& 48.5 MB & 60.8 min & 4.1 min & 1.5 min\\
\bottomrule
\end{tabular}
}

@@

\subsection{Result Overview}
Table~\ref{chapter5:table:over_result} presents the overview result. The minimum unit of the program during the experiment is the function. Suppose the function has more than one access map, then the function that is vulnerable to side-channel attacks. We measure the side-channel leakages at two different granularities: the byte level and the cache line level. The result shows that the program has more leaked vulnerabilities and tends to leak more information at the byte level compare with the cache line level. Each time we run the target program under random inputs and record memory accesses.
